First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-04-06 paper/paper.tex
Restructured section 6 a bit and started to flesh it out

In the technique presented here, we do not need to allocate closures and we
actually do not to use higher-order functions at all.

@@

The standard semantics for the EDSL is given by \ttt{abs}.

@@

prodMatchAbs :: (ERep s)
  => Env
     -> E (ProdMatch s t)
     -> s
     -> t
...

absEnv :: forall t. Env -> E t -> t
absEnv env (CaseExp x f) =
  sumMatchAbs f (absEnv env x)

@@

>>>>

In the technique presented here, we do not need to allocate thunks or closures.
We actually do not to use higher-order functions at all in this tail recursion
representation.

@@

The standard semantics for the EDSL is given by \ttt{abs}. Two helper
functions, \ttt{sumMatchAbs} and \ttt{prodMatchAbs}, are used to provide
the standard semantics for matches on sum types and matches on product
types, respectively. These helper functions are based on the mechanism
described in section 3.4.

@@

prodMatchAbs :: (ERep s)
  => Env
     -> E (ProdMatch s t)
     -> s
     -> t
...
\end{lstlisting}

See Appendix A for more implementation details of \ttt{absEnv}.

@@

\appendix
\section{Additional Code for Standard Haskell Semantics Implementation}
\begin{lstlisting}
absEnv :: forall t. Env -> E t -> t
absEnv env (CaseExp x f) =
  sumMatchAbs f (absEnv env x)
